\chapter{Unit Tests}
\section{C++ Unit Tests}
Initially, the aim was to have unit tests running for the C++ code written for rootJS. 
Google Test was chosen for unit testing. However, an insurmountable issue appeared.
It was not possible to make Google Test work with rootJS, because all files included in
the rootJS source files also had to be built. This includes ROOT and Google v8. ROOT was built just fine, 
but it was not possible to build v8. This was not an issue with Google Test, but an issue with 
v8 itself. There may have been a possibility to build v8, but there little to no documentation 
about how to do it, and would have taken up a considerable amount of time. 
Consequently, rootJS has no unit testing.

\section{JavaScript Tests}
While there are no C++ tests, it is possible to gain significant coverage by using
JavaScript Tests. Mocha is the JavaScript testing framework used for rootJS. 
Mocha runs on Node.js and explicitly supports asynchronous testing, meaning it is ideal for testing 
rootJS' asynchronous capabilities.
\\ \\
Miscellaneous
\begin{itemize}
\item should be possible to have non pointer references to returned objects from function calls
\end{itemize}
Functions overloading

\begin{itemize}
\item should not be possible to call Printf without the corect args
\item should return a number when calling Hash on a string
\item should be possible to call a function that returns a char*
\item should be possible to call a function with a callback that is called when the root code has been processed
\end{itemize}
Interface require
\begin{itemize}
\item should return an object
\end{itemize}
Globals/numbers
\begin{itemize}
\item should have a property named kMaxChar
\item should have kMaxChar which equals 128
\item should save gDebug as an integer (drop decimal values)
\item should overflow silently
\item should not accept values that are not numeric
\item should have a property named kInitTreatAsZero
\item should have kInitTreatAsZero which equals 1e-12
\item should have kInitTreatAsZero which equals 1e-12
\item should fail to write to const globals strings
\item should have the gProgName "node"
\item should consider char pointers to be immutable
\end{itemize}
Booleans
\begin{itemize}
\item should have kTRUE which should be true
\item should have kFALSE which should be false
\item should fail to change the value of kFALSE
\end{itemize}
Functions test
\begin{itemize}
\item should not be possible to call Printf without the corect args
\item should not be possible to call gSystem.Dump without the corect args
\item should have gSystem.ProcessEvents returning a boolean value
\item should be possible to call virtual methods
\item should be possible to call methods asynchronously
\item should be possible to get return values as a param of a callback function
\item should be possible to run multiple functions asynchronously in parallel
\end{itemize}
Constructor
\begin{itemize}
\item should be possible to create a new TString
\end{itemize}
Function return values
\begin{itemize}
\item boolean values should be returned even though they are false
\end{itemize}
